---
title: "PES1UG20CS596"
author: "Srinandan A"
date: "2022-10-15"
output:
  word_document: default
  pdf_document: default
---

#PROBLEM 0

```{r}
library(tidyverse)
library(fpp2)
library(forecast)
library(MLmetrics)

df <- read_csv("C:/Users/srina_1pv/Downloads/DA Assignment/35-Basic Forecasting Techniques/sales.csv")
head(df)

sales <- df$Sales
head(sales)

sales_ts <- ts(sales, frequency = 52, start=c(2010, 2, 5))
sales_ts
plot.ts(sales_ts)
```

We have imported the necessary libraries and read the data set.

#PROBLEM 1

```{r}
components = decompose(sales_ts)
plot(components)
```

We have decomposed the time series dataset into its components and plotted them.

#PROBLEM 2

```{r}
plot(sales_ts)
SEM = HoltWinters(sales_ts, beta = FALSE, gamma = FALSE)
lines(SEM$fitted[,1], lty=2, col="red")

DEM = HoltWinters(sales_ts, gamma = FALSE)
lines(DEM$fitted[,1], lty=2, col="blue")

TEM = HoltWinters(sales_ts)
lines(TEM$fitted[,1], lty=2, col="green")
```

We have plotted the forecasts made using SEM, DEM, and TEM for the given data set.

#PROBLEM 3

```{r}
REG = lm(formula = Sales ~ Holiday_Flag+Temperature+Fuel_Price+CPI+Laptop_Demand, data = df )
summary(REG)

plot(x = df$Sales, y = REG$fitted.values, xlab = "Actual Values", ylab = "Model Values",
     main = "Regression fit")
abline(b = 1, a = 0)
```

We have plotted the forecasts made using regression and plotted it.

#PROBLEM 4

```{r}
demand <- ts(df$Laptop_Demand, frequency = 52)
plot.ts(demand)

x = ma(demand, order = 4)
lines(x, col = "blue")
plot(forecast(x,143))
```

We have plotted the forecast of the laptop_demand column of the dataset.

#PROBLEM 5

```{r}
MAPE(REG$fitted.values,sales_ts)
MAPE(SEM$fitted[,1],sales_ts)
MAPE(DEM$fitted[,1],sales_ts)
MAPE(TEM$fitted[,1],sales_ts)

RMSE(REG$fitted.values,sales_ts)
RMSE(SEM$fitted[,1],sales_ts)
RMSE(DEM$fitted[,1],sales_ts)
RMSE(TEM$fitted[,1],sales_ts)
```

The order of the forecasts which worked best for the given data set are:
1) Triple Exponential Smoothing
2) Regression
3) Single Exponential Smoothing
4) Double Exponential Smoothing 

TEM takes into account that seasonal effect when predicting new values. Hence, it is the best model for sales data as sales data generally have a significant seasonal component.

Both SEM and DEM do not take into account the seasonal effect when predicting new values. Hence, they perform similarly.
