---
title: "PES1UG20CS596"
author: "Srinandan A"
date: "2022-08-28"
output: word_document
---

#LOADING LIBRARIES

```{r}
library(tidyverse)
library(dplyr)
library(ggpubr)
library(ggplot2)
library(ltm)
library(psych)
```

#READING DATA

```{r}
data<-read.csv("C:/Users/srina_1pv/Downloads/DA Assignment/Correlation Analysis/road_accidents_india_2016.csv")
```

#PROBLEM 1

```{r}
data1<-data[grep("Accidents", names(data))]
data$Total.Accidents<-rowSums(data1)
data.frame(data$State..UT, data$Total.Accidents)

data2<-data[grep("Killed", names(data))]
data$Total.Killed<-rowSums(data2)
data.frame(data$State..UT, data$Total.Killed)
```

Here, we have used the grep() function to filter out data from the column names that contain the word "Accidents".

#PROBLEM 2

```{r}
data$Fatality.Rate<-(data$Total.Killed/data$Total.Accidents)
data$Mist..Foggy...Rate<-(data$Mist..Foggy...Total.Accidents/data$Total.Accidents)
data.frame(data$State..UT, data$Mist..Foggy...Rate)

a<-data$Mist..Foggy...Rate
b<-data$Fatality.Rate
ans<-cor(a, b, method = "pearson")

plot(x = data$Mist..Foggy...Rate, y = data$Fatality.Rate, main = "Scatter plot", xlab = "Misty/Fog Rate", ylab = "Fatality Rate", col = "blue")
```

Here, we can see that the correlation factor between fatality rate and misty/foggy condition is 0.2935. 
I couldn't use the ggscatter() function as the package required was not working properly.

#PROBLEM 3

```{r}
data$Rank.Accidents <- rank(desc(data$Total.Accidents), ties.method="first")
data3<-data.frame(data$State..UT, data$Rank.Accidents)
data3[order(data$Rank.Accidents, decreasing = FALSE), ]

data$Rank.Killed <- rank(desc(data$Total.Killed), ties.method="first")
data4<-data.frame(data$State..UT, data$Rank.Killed)
data4[order(data$Rank.Killed, decreasing = FALSE), ]

c<-data$Rank.Accidents
d<-data$Rank.Killed
res<-cor(c, d, method = "spearman")

t <- (res-0.2)/sqrt((1-(res**2))/(nrow(data)-2))
print(2*pt(q=t, df=nrow(data), lower.tail = FALSE))
```

As we can see, the correlation is significantly lesser than 0.2.

#PROBLEM 4

```{r}
data$Hail.Sleet...Occur<-factor(ifelse(data$Hail.Sleet...Total.Accidents==0,"0","1"))
biserial.cor(data$Rainy...Total.Accidents, data$Hail.Sleet...Occur)
data$Dust.Storm...Occur<-factor(ifelse(data$Dust.Storm...Total.Accidents==0,"0","1"))

```

We can see that there exists a -ve correlation between Hail.Sleet...Occur and Total.Accidents.

#PROBLEM 5

```{r}
df<-data.frame(data$Hail.Sleet...Occur, data$Dust.Storm...Occur)
matrix<-table(df)
phi(matrix, digits = 3)
```

As we can see the phi coefficient obtained is 0.622.
