---
title: "PES1UG20CS596"
author: "Srinandan A"
date: "2022-09-17"
output: pdf_document
---

```{r}
#PROBLEM 0
library(ggplot2)
df <- read.csv("C:/Users/srina_1pv/Downloads/DA Assignment/2a (Lecture hour 19)/dragon_neurons.csv")
```

Importing necessary libraries and reading csv file.

```{r}
#PROBLEM 1
lm <- lm(formula = conduction_velocity ~ axon_diameter, data = df)
summary(lm)

ggplot(df, aes(x=axon_diameter, y=conduction_velocity), col="blue") + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```

Yes, a linear model is appropriate for representing the relationship between the conduction velocity
(response variable) and axon diameter (explanatory variable).

```{r}
#PROBLEM 2
res <- resid(lm)
plot(fitted(lm), res, col="blue")
abline(0,0)
qqnorm(res)

df_new<-log(df$axon_diameter)
plot(df_new, res, col="blue")
abline(0, 0)
```

As we can see, there is not much white noise in the given data set.

```{r}
#PROBLEM 3
model <- df[c("axon_diameter" ,"conduction_velocity")]
center <- colMeans(model)
cov <- cov(model)
rad <- sqrt(qchisq(p=0.95, df=2))

ellipse <- car::ellipse(center=center, shape=cov, radius=rad, segments=150, draw=FALSE)
ellipse <- as.data.frame(ellipse)
colnames(ellipse) <- colnames(model)

ggplot(model , aes(x=axon_diameter, y=conduction_velocity)) +
  geom_point(size = 2) +
  geom_polygon(data=ellipse , fill="blue", color="blue", alpha=0.5) +
  geom_point(aes(center[1] , center[2]) , size=5 , color="red") +
  geom_text(aes(label=row.names(model)), hjust=1, vjust=-1.5, size=2.5)
distances <- mahalanobis(x = model , center = center , cov = cov)
distances
cutoff <- qchisq(p = 0.95 , df = ncol(model))
model[distances > cutoff ,]
```

Yes, there are a few outliers in the given data set.

```{r}
#PROBLEM 4
summary(lm)$r.squared 
```

The r-squared value is a indicator of how good our model is. In this case, our model is correct about around 76.56% of the data.

```{r}
#PROBLEM 5
summary(lm)
```

We can say that the conuction velocity is influenced significantly by the axon diameter by looking at the f value, p value and significance codes in the above summary.
