---
title: "PES1UG20CS596"
author: "Srinandan A"
date: "2022-09-17"
output: pdf_document
---

```{r}
#PROBLEM 0
library(tidyverse)
library(corrplot)
library(olsrr)
library(caret)
library(caTools)
df <- read.csv("C:/Users/srina_1pv/Downloads/DA Assignment/2b - MLR (Lecture Hour 25)/spotify.csv")
```

Importing required libraries and reading the csv file.

```{r}
#PROBLEM 1
summary(is.na(df))
sum(is.na(df))
df_new <- data.frame(scale(df)) 
```

There are no NA values. Hence, we normalize the dataset and proceed.

```{r}
#PROBLEM 2
model_full <- lm(energy~ ., data = df)
summary(model_full)
```

Residuals: As we can see there is quite a bit of error in our model.  
t value: The t values of some of the features are greater than 2 or lesser than -2. We can say that those features will most likely be predictors of the target variable.
Pr(>|t|): Some of the p values are less than the confidence interval 0.05. We can say that those features will most likely be predictors of the target variable.
R-Squared: 0.844 signifies that our model explains around 84.4% of the data.
Adjusted R-Squared: Same as R-squared but takes into account how many samples you have and how many variables you’re using.
The F-Statistic: The f statistic being quite a large value tells us that there is some significant feature in our model.

```{r}
#PROBLEM 3
res<-cor(df)
corrplot(res, method="pie")
ols_plot_added_variable(model_full, print_plot = TRUE)

df_new<-data.frame(df$danceability, df$acousticness, df$loudness, df$valence, df$energy)
model_reduced = lm(df.energy~ ., data = df_new)
summary(model_reduced)
```

I chose the features mentioned above after considering the f values, p values, correlogram and scatter plot. All of them signify that these are the most significant features.
The summary of the model confirms my choice(See f values, p values and significance codes).

```{r}
#PROBLEM 4
anova(model_reduced, model_full)
```

H0: All coefficients removed from the full model are zero.
HA: At least one of the coefficients removed from the full model is non-zero.


```{r}
#PROBLEM 5
model_aic <- ols_step_backward_aic(model_full)
plot(model_aic)
summary(model_aic$model)
```

As we can see from the graph, the Aic model removes a few features step by step and retains a few features in the end. It contains a couple more features than my reduced model with my features of choice.

```{r}
#PROBLEM 6
ols_plot_resid_hist(model_full, print_plot = TRUE)
ols_plot_resid_hist(model_reduced, print_plot = TRUE)
ols_plot_resid_hist(model_aic$model, print_plot = TRUE)
```

As we can see, the models we built are pretty accurate (around 84%), the best one being the AIC model. We can also say that the variance of the models are normally distributed.

```{r}
#PROBLEM 7
ols_vif_tol(model_full)
ols_plot_cooksd_bar(model_full)
ols_plot_cooksd_chart(model_full)

cooksd = cooks.distance(model_full)
plot(cooksd)

n = nrow(df)
infl <- as.numeric(names(cooksd)[(cooksd > (4/n))])

df = df[-infl,]
view(df)
model_full = lm(energy~acousticness+danceability+loudness+valence,data=df)
summary(model_full)
anova(model_full)
ols_plot_cooksd_chart(model_full)

cooksd2 = cooks.distance(model_full)
plot(cooksd2)
```

As we can see, the model of the new data set is slightly better.
